### 2024-05-16 thesis/chapters/05-evaluation.tex
Final

\section{Fault classifiction in MaFaulDa}
The four outlined experiments on MaFaulDa involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum. First, the attributes are left in the complete count after extraction. Then, all of their combinations are enumerated, and the resulting accuracy distribution is matched against accuracy after feature selection with similarity metrics.

@@

The label ``normal'' is not falsely attributed to other classes in either feature set, but other classes can get assigned to be ``normal''. Most mistakes happen while predicting outer race fault, which is confused with cage fault, imbalance, and less often with misalignment. The shaft imbalance is used for simulating bearing faults, which is a natural reason for this high error rate.

@@

The increasing number of neighbours used for classification in 5-fold cross-validated k-NN shows a substantial decrease in accuracy on validation sets (Fig.~\ref{fig:evaluation:complete-set-k-value}). The most prominent drop in performance of around 10\% occurs at the beginning until the k-value of nine, and then the accuracy curves slowly plateau.

Under every circumstance, the magnitude of the triaxial feature vector reaches better accuracy than those from only the axis of motion for the same source domain and bearing. The model for inner bearing A is more accurate than outer bearing B. The TD set is generally better in predictions than the FD set for the equivalent k-value. The relabeled dataset for high severity has a steeper decrease in accuracy for the same number of neighbours.

\subsection{Feature subset combinations}
The complete sets of predictors are even greatly shrunken to representation that could be presented in 3D plot or in perpendicular cross sections. These trend variables could be used in distinguishing faults the same way as rms amplitude indicates their presence. Each possible combinations of pairs, triplets, and quadruplets constructs a separate k-NN model on which prediction accuracy is evaluated.

@@

The distribution of model accuracies is documented on features in both domains coined from three dimensions on bearing A with original and high-severity defect labels. The boxplots display the relation of the k-value to accuracy when three features are chosen, and the relation of a number of features to accuracy with five neighbours(Fig.~\ref{fig:evaluation:model-accuracy-severity} and \ref{fig:evaluation:model-accuracy-severity}).

The decrease in accuracy with additional neighbours is apparent and similar to the trend in complete sets of features. We are interested in comparing maximum accuracies of the accuracy distribution because the optimal feature selection method tries to approach them. The reduction in maximal accuracy is more noticeable between three and five features 3 - 5\%, and almost the same amount between five and eleven neighbours.

@@

The spread in model accuracies in the interquartile range is from 5 to 10 \%, and measured between whiskers is at a maximum of 25\%. The standard deviation is about 7\%. Overall, the time-domain features are better than frequency-domain features for these specific feature spaces.

The number of features has a direct proportionality effect on the optimal model accuracy. An increase from two to three features has more weight than allowing a fourth attribute. The contributions of adding features are around 6\% and 3\%, and the relabeled dataset has an increase of 3\% and 2\%. The absolute accuracies are consecutively for 2, 3, and 4 features when k is equal to 5: 78.31\%, 85.67\%, and 89.55\% for the time domain and 81.52\%, 87.52\%, 90.26\% in the frequency domain.

\subsection{Feature selection techniques}
The predictors chosen with supervised selection strategies are compared in accuracy and location within the accuracy distribution of exhaustive combinations of same-sized sets and the performance of its source superset. The metrics for bivariate feature selection are correlation, F statistic, mutual information, and their ensemble by the rank product. The PCA of the complete feature set that retains the same number of features and selection methods serves as a benchmark to tell whether the linear combination or subset gets better performance on the MaFaulDa.

@@

Table~\ref{tab:evaluation:fsel} compares the concrete case of choosing the three features from each domain on bearing A and k-NN with five neighbours. Table~\ref{tab:evaluation:fsel-severity} uses labels for high-severity faults. There is a significant difference in train and test accuracy, which means the model is likely overfitting. The percentile within the distribution is measured to its respective data, the train or validation set. However, the percentile of best features in the test data is calculated against train distribution.

Combining the rankings from several metrics is necessary to get consistent results. This is evidenced by the variability of the success of selected feature sets in final prediction performance under multiple conditions. The PCA with 3 components transformed from the complete feature sets is comparable in accuracy to selection methods with original attributes.

The triplet of variables with the best results is from TD set: zero-crossing rate, peak-to-peak, skewness, and from FD set: centroid, roll-off, and entropy. With high severity labels, the best attributes for FD stay the same, but average amplitude change and shape factor are preferred along the zero-crossing rate. The rank product picked up roll-off, flux, and skewness for the FD set, which is suboptimal. The two of the three methods in the ensemble arrive at the same set overruling the superior set produced by mutual information. In the TD set, the zero-crossing rate, shape, and rms, are chosen by rank product.

@@

The entire accuracy distribution for the training and testing set for original labels is drawn in the form of the histogram (Fig.~\ref{fig:evaluation:fsel-model-distr}). The results of the chosen predictors are mapped out onto the distribution as vertical lines that stack up near the maximum for the time domain or disperse slightly above the median for the frequency domain. The accuracy of all features is unreachable for three feature subsets. Another noticeable difference between distributions is their shift down and greater spread in testing compared to training sets.

@@

Kernel density estimate plot (Fig.~\ref{fig:evaluation:kde-fsel-perecentile}) shows the distribution of accuracies for the selection methods and percentiles for predictor subsets they chose. The feature selection usually picks variables so that they stay in the upper quartile of the distribution above the 75\% percentile. The median accuracy of all methods is around the vicinity of 80\%.

@@

The k-NN models in incremental learning experiments learn on the same base training dataset as in batch learning for bearing A. Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced. In this manner, we can compare the training accuracies in the last sample of online models to their batch counterparts.

@@

A significant change in the data stream occurs after 294 out of 1438 observations (or after 737 for high severity faults) when all 49 (or 737) normal conditions are consumed in the training process. Counters of other faults show that predictions are skewed towards more represented classes of imbalance and misalignment. The uneven evolution of categories in a stream impacts the development of accuracy in the remaining experiments. The test accuracies of comparable batch models from the three best features are 85.47\% (TD), 87.52\% (FD), 91.71\% (TD severity), and 91.94\% (FD severity).

\begin{figure}[]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Tumbling window during incremental learning of lengths 1, 10, 100}
    \label{fig:evaluation:tumbling-window-online}
\end{figure}

@@

Labeling every \nth{10} sample (10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels. Time-domain features it is decreased by 9.9\% to 66.78\%, and by 14.93\% for frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}). More annotations can be scrapped in the case of a relabeled dataset where keeping just 0.02\% of the class labels produces a decrease by 13.7\% to 68.79\% for time domain attributes, and by 16.59\% to 66.25\% for frequency domain attributes.

\section{Industrial dataset analysis}
The latter part of the solution evaluation focuses on signal properties of vibrations from air compressors, water pumps, and electric induction motors. At first, the accelerometer data logger functionality is tested, and its precision is checked up in the known situations. Our custom dataset is compiled from collected measurements during regular operations of machines. The behaviour of different machines is compared using static frequency estimation and a time-frequency spectrogram. The domain expert methodology is carried out to diagnose the current status of water pumps. The presence of fault is confronted with sensor logs from the pump vendor.

\subsection{Data logger verification}
Data logger capabilities were verified by capturing vibrations on the back of the plastic casing for the electric motor of the standing fan. The recording is able to run continuously for more than one minute without dropping any samples. The amplitude range after conversion is constrained in the expected range (Fig.~\ref{fig:evaluation:logger-waveform}). The same amplitudes were obtained previously on a proof-of-concept device using analog accelerometer ADXL335 on Beaglebone Black, albeit with lower sensitivity.

@@

Domain experts recommended the procedure for fault identification by calculation of bearing characteristic frequencies (Tab.~\ref{tab:evaluation:bearing-freq-pump}), and they approved the following results. Figure~\ref{fig:evaluation:bearing-freq} identifies harmonics of rotational speed and BPFO frequency in every machine and BPFI for M2-2. It can be assumed that those frequencies will be the reason for damage in the future. The absolute acceleration is minuscule in current frequency bands and year-long sensor log of rms velocity (Fig~\ref{fig:evaluation:ksb-guard-rms-vibartions}).

@@

Therefore, the current results suggest that the bearings are in flawless condition. During the over five years the pump has been in service, there is not one instance of bearing fault due to rated lifespan and yearly prophylactic maintenance. This underscores the scarcity of recording faulty states in industrial environments. The monitoring is better suited for situations without preventive maintenance or with smaller machinery like the plunger pump BC~21/20S we considered during air conditioning inspections.

@@

Spectrograms point out that under constant machine load, the significant frequencies stay more or less unchanged over time (Fig~\ref{fig:evaluation:spectrograms}). The resolution of the chart unit area is 306.95 ms and 3.26 Hz. Its magnitude is colored for decibel value.

@@

The water pump switch on and off creates a fast change in shaft speed, which cannot be analyzed for resonance bands with enough time resolution by an automatic system at a chosen sampling rate. Due to inertia, slowing down takes about 10 seconds, whereas the speed up is half a second (Fig.~\ref{fig:evaluation:pump-switch-over}. The interference from excessive vibrations of the adjacent Sigma pump is picked up by the accelerometer on the KSB pump just before their switchover occurs (Fig~\ref{fig:evaluation-sigma-pump-interference}).

@@

The range of feature values for compressors and pumps are higher than in MaFaulDa despite most of them describing baseline status (Fig~\ref{fig:evaluation-sigma-pump-interference}). The increases can be seen for example on the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).

>>>>

\section{Fault classifiction in MaFaulDa}
The four outlined experiments on MaFaulDa involve testing sets of features with very few members. The effect in predictions is observed when reducing the information content about machine's status to the minimum. First, the attributes are left in full after extraction. Then, all of their combinations are enumerated, and the resulting accuracy distribution is matched against accuracy after feature selection with similarity metrics.

@@

The label ``normal'' is not falsely attributed to other classes in either feature set, but other classes can get assigned to be ``normal''. Most mistakes happen while predicting outer race fault, which gets confused with cage fault, imbalance, and less often with misalignment. The shaft imbalance is applied to simulate bearing faults, which is a natural reason for this high error rate.

@@

An increase in the number of neighbours used for classification in five-fold cross-validated k-NN shows a substantial decrease in accuracy on validation sets (Fig.~\ref{fig:evaluation:complete-set-k-value}). The most prominent drop in performance of around 10\% occurs at the beginning until the k-value of nine, and then the accuracy curve slowly plateaus.

Under every circumstance, the magnitude of the triaxial feature vector reaches better accuracy than those from only the axis of motion for the same source domain and bearing. The model for inner bearing A is more accurate than outer bearing B. The TD set is generally better in predictions than the FD set for the equivalent k-value. The dataset relabeled for high severity has a steeper decrease in accuracy for the same number of neighbours.

\subsection{Feature subset combinations}
The complete sets of predictors are even greatly shrunken to representation that could be presented in 3D plot or in perpendicular cross sections. These trend variables could be used in distinguishing faults the same way as rms amplitude indicates their presence. Each possible combinations of pairs, triplets, and quadruplets construct a separate k-NN model on which prediction accuracy is evaluated.

@@

The distribution of model accuracies is documented on features in both domains coined from three dimensions on bearing A with original and high-severity defect labels. The boxplots display the relation of the k-value to accuracy with three features, and the relation of number of features to accuracy with five neighbours (Fig.~\ref{fig:evaluation:model-accuracy-severity} and \ref{fig:evaluation:model-accuracy-severity}).

The decrease in accuracy with additional neighbours is apparent and similar to the trend in complete sets of features. We are interested in comparing maximum accuracies of the accuracy distribution because the optimal feature selection method tries to approach them. The reduction in maximal accuracy is more noticeable between three and five features of 3\% to 5\%, and almost the same amount between five and eleven neighbours.

@@

The spread in model accuracies in the interquartile range is from 5 to 10\%, and measured between whiskers is 25\% at a maximum. The standard deviation is about 7\%. Overall, the time-domain features are better than frequency-domain features for these specific feature spaces.

The number of features has a direct proportionality effect on the optimal model accuracy. An increase from two to three features has more weight than allowing a fourth attribute. The contributions of adding features are around 6\% and 3\%, and the relabeled dataset has an increase of 3\% and 2\%. The absolute accuracies are consecutively for 2, 3, and 4 features when k is equal to 5: 78.31\%, 85.67\%, and 89.55\% for the time domain and 81.52\%, 87.52\%, 90.26\% for the frequency domain.

\subsection{Feature selection techniques}
The predictors chosen with supervised selection strategies are compared to the accuracy distribution of  enumerated combinations of same-sized attribute sets and the performance of its source superset. The metrics for bivariate feature selection are correlation, F statistic, mutual information, and their ensemble by the rank product. The PCA of the complete feature set that retains the same number of features as a selection method is a benchmark to tell whether the linear combination or meaningful attributes get better performance on the MaFaulDa.

@@

Table~\ref{tab:evaluation:fsel} compares the concrete case of choosing the three features from each domain on bearing A and k-NN with five neighbours. Table~\ref{tab:evaluation:fsel-severity} uses labels for high-severity faults. There is a significant difference in train and test accuracy, which means the model is likely overfitting. The percentile within the distribution is measured to its respective data, the train or validation set. However, the percentile of best features in the test data is calculated against distribution of the training data.

Combining the rankings from several metrics is necessary to get consistent results. This is evidenced by the variability in the success of selected feature sets in final prediction performance under multiple conditions. The PCA with three components for the complete feature sets is comparable in accuracy to selection methods with original attributes.

The triplet of variables with the best results is in TD set: zero-crossing rate, peak-to-peak, skewness, and in FD set: centroid, roll-off, and entropy. With high severity labels, the best attributes for FD stay the same, but average amplitude change and shape factor are preferred along the zero-crossing rate. The rank product picked up roll-off, flux, and skewness for the FD set, which is suboptimal. The two of the three methods in the ensemble arrive at the same set overruling the superior set produced by mutual information. In the TD set, the zero-crossing rate, shape, and rms, are chosen by rank product.

@@

The entire accuracy distribution for the training and testing set with original labels is drawn as a histogram (Fig.~\ref{fig:evaluation:fsel-model-distr}). The results of the chosen predictors are mapped out onto the distribution as vertical lines that stack up near the maximum for the time domain or disperse slightly above the median for the frequency domain. The accuracy of all features is unreachable for three feature subsets. Another noticeable difference between distributions is their shift down and greater spread in testing sets compared to training sets.

@@

Kernel density estimate plot (Fig.~\ref{fig:evaluation:kde-fsel-perecentile}) shows the distribution of accuracies for the selection methods and percentiles for predictor subsets they choose. The feature selection usually picks variables so that they stay in the upper quartile of the distribution above the 75\% percentile. The median accuracy of all methods is the vicinity of 80\%.

@@

The k-NN models in incremental learning experiments train on the same base training dataset as those in batch learning for bearing A. Online learning metrics are evaluated by progressive valuation on a still unbalanced dataset. In this manner, we can compare the training accuracies for the last sample of online models to their batch counterparts.

@@

A significant change in the data stream occurs after 294 out of 1438 observations (or after 737 for high severity faults) when all 49 (or 737) normal conditions are consumed in the training process. Counters of other faults show that predictions are skewed towards more represented classes of imbalance and misalignment. The uneven evolution of categories in a stream impacts the evolution of accuracy in the remaining experiments. The test accuracies of comparable batch models for three best features are 85.47\% (TD), 87.52\% (FD), 91.71\% (TD severity), and 91.94\% (FD severity).

\begin{figure}[]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Tumbling window of lengths 1, 10, 100 during incremental learning}
    \label{fig:evaluation:tumbling-window-online}
\end{figure}

@@

Labeling every \nth{10} sample (10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels. In time-domain features, it is decreased by 9.9\% to 66.78\%, and by 14.93\% in frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}). More annotations can be scrapped in the case of a relabeled dataset where keeping just 0.02\% of the class labels produces a decrease by 13.7\% to 68.79\% for time domain attributes, and by 16.59\% to 66.25\% for frequency domain attributes.

\section{Industrial dataset analysis}
The latter part of the solution evaluation focuses on signal properties of vibrations from air compressors, water pumps, and electric induction motors. Our custom dataset is compiled from measurements collected during regular operation of machines. The behaviour of different machines is compared using static frequency estimation and a time-frequency spectrogram. The domain expert methodology is carried out to diagnose the current status of water pumps. The presence of fault is confronted with sensor logs from the pump's vendor.

\subsection{Data logger verification}
Data logger capabilities were verified by capturing vibrations on the back of the plastic casing for the electric motor of the standing fan. The recorder is able to run continuously for more than one minute without dropping any samples. The amplitude range after conversion is constrained in the expected range (Fig.~\ref{fig:evaluation:logger-waveform}). The same amplitudes were obtained previously on a proof-of-concept device using analog accelerometer ADXL335 on Beaglebone Black, albeit with lower sensitivity.

@@

Domain experts recommended the procedure for fault identification by calculation of bearing characteristic frequencies (Tab.~\ref{tab:evaluation:bearing-freq-pump}), and they approved the following results. Figure~\ref{fig:evaluation:bearing-freq} identifies harmonics of rotational speed and BPFO frequency in every machine and BPFI for M2-2. It can be assumed that those frequencies will be the reason for damage in the future. The absolute acceleration is minuscule in current frequency bands and year-long sensor logs of rms velocity (Fig~\ref{fig:evaluation:ksb-guard-rms-vibartions}).

@@

Therefore, the current results suggest that the bearings are in flawless condition. During the over five years the pumps have been in service, there is not one instance of bearing fault due to rated lifespan and yearly prophylactic maintenance. This underscores the scarcity of recording faulty states in industrial environments. The monitoring is better suited in situations without preventive maintenance or with smaller machinery like the plunger pump BC~21/20S we considered during air conditioning inspections.

@@

Spectrograms point out that under constant machine load, the significant frequencies stay more or less unchanged over time (Fig~\ref{fig:evaluation:spectrograms}). The resolution of the uncertainty box is 306.95 ms and 3.26 Hz. Its magnitude is colored for decibel value.

@@

The water pump switch on and off creates a fast change in shaft speed. Resonance bands cannot be separated with enough time resolution by an automatic system at a chosen sampling rate. Due to inertia, slowing down takes about 10 seconds, whereas the speed up takes just half a second (Fig.~\ref{fig:evaluation:pump-switch-over}. The interference from excessive vibrations of the adjacent Sigma pump is picked up by the accelerometer on the KSB pump just before their switchover occurs (Fig~\ref{fig:evaluation-sigma-pump-interference}).

@@

The range of feature values for compressors and pumps are higher than in MaFaulDa despite most of them describing baseline status (Fig~\ref{fig:evaluation-sigma-pump-interference}). The increase can be seen for example in the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).

### 2024-05-16 thesis/chapters/06-conclusion.tex
Final

\chapter{Conclusion} \label{section:conclusion}  
In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals. The goal is to enable timely fault detection of machinery parts with as little input data as possible. For that purpose, we answer four research questions.

Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343). These formulas compute ten features summarizing the waveform in the temporal domain and eleven features characterizing spectral density estimation in axis of motion or all three spatial directions \textbf{(RQ1)}.

In order to achieve more pronounced data savings, we choose the subset of 3 features in each domain by keeping the ones with the most similarity to the target variable. Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are applicable in supervised learning. The features are squished from multiple dimensions using the Euclidian norm. Lossy compression ratios attained are 2381:1 for all features and 25000:1 for 6 features in the MaFaulDa dataset. We managed to discard more than 99.995\% of irrelevant data \textbf{(RQ2)}.

Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power. Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%. The time-domain set of features reach higher accuracies than frequency-domain set because of their smaller interdependency \textbf{(RQ3)}.

The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations. No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively. 
%TODO wtf
Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.

The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables. Annotations can be assigned belatedly or even never. Incremental learning k-NN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label. The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

The vibration signals will be gathered on compressors in air conditioning units and water pumps in municipal pumping stations. We will develop firmware for sensor units capable of sampling accelerometers and saving measurements onto SD cards. The challenge awaits us in labeling samples themselves as it requires substantial expert knowledge.

%TODO
% Future work
% - long term dataset from machinery until failure or propose way for factories to artifically train model for new machinery - make the system machine and placement independent
% - more diffenent feature set from one recoding - in windows
% - combine feature selection with incremntal learining
% - Different election methods and metrics
% - Find other ML model also suitable HoeffdingTreeClassifier - losing original data for labeling - mechnaism of transforming samples to model represntatin
% - Monitor more machines and combine their result with federated learning
% - Monitor faults of different equipment - moving wheels of the train or train tracks

% Main points of the thesis assigments namely effectivness representation of machinery faults in succint fashion and performance in machine learining diagnostics models has been compared extensively.

>>>>

\chapter{Conclusion} \label{section:conclusion}
The focus of this master's thesis is on the optimal choice of trend indicators from vibration signals in an inexpensive industrial condition monitoring solution. The goal is to enable timely fault detection of machinery parts with as little input data as possible. We answer \textbf{five research questions} for those purposes.

\textbf{The first question} is about finding numerical features that can represent machinery behaviour for accurate diagnosis. The technical standards in vibrodiagnostics and the descriptive statistics for time-varying phenomena are valuable in that regard. Vibrations have to be recorded at a high sampling rate. The researched formulas narrow down this massive data stream to groups of a few features. We define ten features that summarize the waveform in the time domain (\emph{TD}) and eleven features that describe its spectral density estimation (\emph{FD}). The features are either just taken from the axis of the jitter, or aggregated from all three spatial directions.

\textbf{The second question} answers the effort to achieve even more pronounced savings in transmission goodput. Groups of three predictors are chosen from each base feature set that together have the most similarity to the target variable. Feature selection scores of the correlation coefficient, F statistic, mutual information, and their rank product are computed in supervised learning scenarios. Lossy compression ratios attained are 2381:1 for all features and 25000:1 for six features from the MaFaulDa dataset. We managed to discard more than 99.995\% of the irrelevant data.

\textbf{The third question} asks about the accuracy of the machine learning model for machinery fault diagnostics. The major constraint put on the model is to provide inference from reduced sets of predictors. The k-nearest neighbours classifier is utilized because it works on a simple to-explain assumption that proximate data points mean the same type of fault. Additionally, the k-NN retains individual historical observations and can be applied in an incremental learning approach.

We implement the \textbf{data processing pipeline} that transforms the MaFaulDa dataset for multiclass classification with the k-NN algorithm and a tiny number of features. The fault labels with severity are composed of the file's path from the dataset structure. The features are extracted from vibration time series after digital filtering. Then, the features are arranged into multiple configurations: complete feature sets, enumerated feature subset combinations, and feature subsets chosen by filtering feature selection methods. The accuracy results are validated by five-fold cross-validation.

We found that for this particular dataset, the chosen time-domain features have reached higher accuracies than the chosen frequency-domain set because of fewer intercorrelations. An increase in k-neighbours lessens the model accuracy because class boundaries overlap and are relatively noisy. Predictors aggregated from tri-axis recording performed better in classification than those from just one axis.

The feature selection methods can pick a group of predictors with accuracy above the upper quartile of the statistical distribution of accuracy values for the same-sized sets. The rank product method found the best-performing attributes in the majority of 44\% of scenarios, closely followed by mutual information. The rank product for the predictor's triplets reaches the 97.50\% percentile from the accuracy distribution.

The number of features has a direct proportionality effect on accuracy. The absolute best predictor triplets for MaFaulDa are in TD (accuracy of 85.47\%): zero-crossing rate, peak-to-peak, skewness, and in FD (accuracy of 87.52\%): spectral centroid, roll-off frequency, and entropy.

\textbf{The fourth question} investigates machinery behavior in an industrial environment using signal processing techniques. The vibrations were collected a month apart by an accelerometer data logger according to the specification. The designated machines were air conditioning compressors and water pumps with motors in municipal pumping station. We implemented a data logger's firmware that reads samples after a button press from the accelerometer at 26.8 kHz and stores them onto a memory card.

Analysis of the collected dataset confirms the stationarity of the signal spectrum under constant load and assures that five-second bursts are indeed satisfactory for feature extraction. The dataset provides a practical exercise in labeling potential future faults from bearing defect frequency amplitudes. It also demonstrates the immense difficulty of obtaining observations of faulty machinery in the field without purposefully damaging it.

\textbf{The fifth question} is concerned with incremental machine learning because the considerable obstacle in the deployment of an autonomous fault detection system is the availability of annotations that can be assigned belatedly or even never. Incremental k-NN algorithm on an unbalanced dataset for three predictors achieves at best 77\% accuracy with labels in tumbling windows of hundred samples. The accuracy of 67\% is reached for the online model when just 10\% of observations stay associated with the label. The comparable model trained in batch reaches an accuracy of 88\%.

\textbf{We conclude} that an inexpensive industrial condition monitoring solution with low data rates is indeed possible. It uses the available accelerometer sensors and feature discovery techniques. According to the analysis, the system could diagnose the machine's health with high accuracy in a local model on the edge device.

\section{Future work}
Future work would focus on the deployment of our machine learning model on a large scale to sensor units and setting up the necessary infrastructure. The components for such an endeavour are described in the analysis for incremental learning. The way to annotate observations could be introduced, either automatically depending on the overall vibration level or manually during maintenance or after an unexpected failure.

The natural research extension of the thesis is to confirm that the results hold in other publicly available datasets of machinery faults, e.g. in CWRU. The other alteration is to use more and different starting base feature sets. Harmonic frequencies or wavelet coefficients can generate predictors that could be reduced further to the smallest possible subsets.

Ensemble strategies inspired by classical election systems may be utilized in the task of feature selection. Different types of classifiers for online learning could be compared to k-nearest neighbours, e.g. Hoeffding tree. A combination of local models from multiple sensors is desirable, e.g. in a federative learning approach.
